Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains

### 2016-10-19 tex/paper.tex
remove revision bolding

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun. \textbf{It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future. \citet{guennou_can_2013} provide an extensive overview of this topic.}

@@

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e. the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are evenly spaced (i.e. $\beta=0$) and chosen from a power-law distribution of $\alpha=-1.5$. The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

@@

	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures. \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding. The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively. The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here. The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV. The second and third pairs have similar ratio values. This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}

@@

	\par \textbf{For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band. Given the many uncertainties in the measurements, it is unlikely that any of these line pairs can provide an unequivocal constraint on $t_N$. For $\beta=0$, there is an upturn in the ratio between $t_n = 2000$ s and $3000$ s, and below this value, the ratios are ill-defined due to lack of plasma at one or both of the measured temperatures. At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.} 

@@

	\par \textbf{On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here. In addition, for all line pairs, the detection of an emission measure ratio lying between the upper and lower bounds shown can be regarded as a very strong indicator of the presence of ``hot'' nanoflare-produced plasma. Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.}

>>>>

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun. It should be noted that there can be considerable uncertainties in deriving a reliable $\mathrm{EM}(T)$ distribution from observations due to uncertainties from the atomic physics, line-of sight, loop geometry, etc., which will hopefully be mitigated by improved knowledge of such quantities in the future. \citet{guennou_can_2013} provide an extensive overview of this topic.

@@

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e. the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are evenly spaced (i.e. $\beta=0$) and chosen from a power-law distribution of $\alpha=-1.5$. The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

@@

	\par Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures. \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding. The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively. The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here. The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV. The second and third pairs have similar ratio values. This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.

@@

	\par For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band. Given the many uncertainties in the measurements, it is unlikely that any of these line pairs can provide an unequivocal constraint on $t_N$. For $\beta=0$, there is an upturn in the ratio between $t_n = 2000$ s and $3000$ s, and below this value, the ratios are ill-defined due to lack of plasma at one or both of the measured temperatures. At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.

@@

	\par On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here. In addition, for all line pairs, the detection of an emission measure ratio lying between the upper and lower bounds shown can be regarded as a very strong indicator of the presence of ``hot'' nanoflare-produced plasma. Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.
